---
title: "Project 3"
author: "Alain T Kuiete"
date: "10/17/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
library(dplyr)
library(httr)
library(tidyverse)
library(ggplot2)
library(plotly)
library(tidyr)
```

### Data Science Skills

#### Data Science General Skills

```{r}
text_string <- read_file("https://github.com/AlainKuiete/DATA607/blob/master/datascienceskills")
search_word <- c('python', 'machine', 'learning','analytic', 'team', 'teams', 'r','aql','communicative','communication', 'analytical','java','scala', 'hdoop','spark','computer', 'science', 'communicate','engineering', 'solving', 'Tableau', 'sofware', 'statistical','modeling','quantitative',
'customer', 'statistics', 'management', 'models', 'predictive', 'problems')


Results <- data_frame(text = text_string) %>% 
  mutate(text = tolower(text)) %>% 
  mutate(text = str_remove_all(text, '[[:punct:]]')) %>% 
  mutate(tokens = str_split(text, "\\s+")) %>%
  unnest() %>% 
  count(tokens) %>% 
  filter(tokens %in%search_word) %>%
  mutate(freq = n / sum(n)) %>% 
  arrange(desc(n))
```


### The table with words and frequencies.
```{r}
Results
```




```{r}
ggplot2::ggplot(Results, aes(x=tokens, y=freq, fill=tokens)) + 
  geom_bar(width = 0.75,  stat = "identity", colour = "black", size = 1) + 
  coord_polar(theta = "x") + xlab("") + ylab("") + 
  ggtitle("Word Frequency") + theme(legend.position = "none") + 
  labs(x = NULL, y = NULL)

plotly::ggplotly(ggplot2::ggplot(Results, 
                  aes(x=tokens, y=freq, fill=tokens)) + 
                   geom_bar(width = 0.75, stat = "identity", colour = "black", size = 1) + 
                   xlab("") + ylab("") + ggtitle("Word Frequency") + 
                   theme(legend.position = "none") + 
                   labs(x = NULL, y = NULL) + 
                   theme(plot.subtitle = element_text(vjust = 1), plot.caption = element_text(vjust = 1), axis.text.x = element_text(angle = 90)) + 
                   theme(panel.background = element_rect(fill = "honeydew1"), plot.background = element_rect(fill = "antiquewhite")))%>% 
  config(displaylogo = F) %>% config(showLink = F)
```

##### Downloading data
```{r}
dsg <- read.csv("https://raw.githubusercontent.com/AlainKuiete/DATA607/master/ds_general_skills_revised.csv" )
str(dsg)
```

#### Subsetting the Data Science soft Skills 
```{r}
dskg <-dsg[1:15,]
```

#### reshaping my dataframe
```{r}
colnames(dskg) <- c("D.Skills", "LinkedIn", "Indeed", "SimplyHired", "Monster")
dskg$LinkedIn <- as.numeric(gsub(",","",dskg$LinkedIn))
dskg$Indeed <- as.numeric(gsub(",","",dskg$Indeed))
dskg$SimplyHired <- as.numeric(gsub(",","",dskg$SimplyHired))
dskg$Monster <- as.numeric(gsub(",","",dskg$Monster))
```


#### Computation
```{r}
s.dskg <- summarise(dskg, sL=sum(LinkedIn, na.rm=TRUE), sI= sum(Indeed, na.rm=TRUE), sS=sum(SimplyHired, na.rm=TRUE),
           sM=sum(Monster, na.rm=TRUE))

tsg <- sum(s.dskg)

g.skills <- dskg%>% mutate(D.Skills, pct=(LinkedIn+Indeed+SimplyHired+Monster)/tsg)%>%
  select(D.Skills,pct)
g.skills
```

##### Changing the values of variable D.skill
```{r}
D.Skills.abv <-c("02ml", "01an", "03st", "04cs", "05co", "06ma", "07vi","08ai",
                     "09dl","10nlp", "11sd", "12nn", "13de", "14pm","15se")
g.skild <- data.frame(g.skills,
                      ds.abv = D.Skills.abv,
                      D.Skills = g.skills$D.Skills,
                      pct=g.skills$pct)

```

#### Visualisation

```{r}
ggplot(g.skild, 
       aes(x=ds.abv, y = pct))+
  geom_col(aes(fill=D.Skills), position = "dodge")+
  xlab("Genaral Skills")+ylab("Overall percentage")+
  ggtitle("General Skills for Data Science")
```

#### Analysis, Machine Learning, Statistics, Computer Science and Communication are general skill required for Data Scientists.



#### Data Science Soft Skills

##### Downloading data
```{r}
dss <- read.csv("https://raw.githubusercontent.com/AlainKuiete/DATA607/master/ds_job_listing_software.csv")
```


#### Subsetting the Data Science soft Skills 
```{r}
dsk <- dss[1:30,1:5]
str(dsk)
```

#### reshaping my dataframe
```{r}
colnames(dsk) <- c("D.Skills", "LinkedIn", "Indeed", "SimplyHired", "Monster")
dsk$LinkedIn <- as.numeric(gsub(",","",dsk$LinkedIn))
dsk$Indeed <- as.numeric(gsub(",","",dsk$Indeed))
dsk$SimplyHired <- as.numeric(gsub(",","",dsk$SimplyHired))
dsk$Monster <- as.numeric(gsub(",","",dsk$Monster))
```


#### Computation
```{r}
s.dsks <- summarise(dsk, sL=sum(LinkedIn), sI= sum(Indeed), sS=sum(SimplyHired),
           sM=sum(Monster))
ts <- sum(s.dsks)

skills <- dsk%>% mutate(D.Skills, pct=(LinkedIn+Indeed+SimplyHired+Monster)/ts)%>%select(D.Skills,pct)
skill <-skills[1:10,]
skill
```



#### Visualisation
```{r}

ggplot(skill, 
       aes(x=D.Skills, y = pct))+
  geom_col(aes(fill=D.Skills), position = "dodge")+
  xlab("Computer Skills")+ylab("Overall percentage")+
  ggtitle("Top 10 Sofware Skills for Data Science")
```

### Python and R are the most software computer skills recommanded for Data Scientist.


##### Reference: The Most in Demand Skills for Data Scientists by Jeff Hale. Toward Data Science




```{r}
url1 <- "https://www.google.com/search?safe=active&rlz=1C1EJFC_enUS834US834&sxsrf=ACYBGNSOYZtHkxHTh41kYm0q3DH8TnMuHw:1572152661833&ei=VSW1Xa3EMsHk_Ab9_afoAw&q=data+sciences+jobs&oq=data+sciences+jobs&gs_l=psy-ab.3..0i10l10.41861.55760..56318...1.0..1.3382.6568.0j1j7-1j1j1......0....1..gws-wiz.....10..35i362i39.rCNbLJ7wjdA&uact=5&ibp=htl;jobs&sa=X&ved=2ahUKEwjMi9q01bvlAhWCm-AKHSUxD-wQp4wCMAB6BAgFEAE#fpstate=tldetail&htidocid=n1I1nIYsv9Heqo3hAAAAAA%3D%3D&htivrt=jobs"
```


### counting words with R
```{r}
url2 <- "https://www.codementor.io/jhwatts2010/counting-words-with-r-ds35hzgmj"
```
